---
title: "Untitled"
output: html_document
date: "2024-03-23"
---

```{r setup, include=FALSE}
# Get the Data
key_crop_yields <- read.csv('key_crop_yields.csv')
fertilizer <- read.csv('cereal_crop_yield_vs_fertilizer_application.csv')
land_use <- read.csv('land_use_vs_yield_change_in_cereal_production.csv')
arable_land <- read.csv('arable_land_pin.csv')
```
```{r}
kcy = subset(key_crop_yields, key_crop_yields$Code == "" & key_crop_yields$Entity != "Belgium-Luxembourg" & key_crop_yields$Entity != "Ethiopia PDR" & key_crop_yields$Entity != "European Union" & key_crop_yields$Entity != "Land Locked Developing Countries" & key_crop_yields$Entity != "Least Developed Countries" & key_crop_yields$Entity != "Low Income Food Deficit Countries" & key_crop_yields$Entity != "Net Food Importing Developing Countries" & key_crop_yields$Entity != "Pacific Islands Trust Territory" & key_crop_yields$Entity != "Small island developing States" & key_crop_yields$Entity != "Sudan (former)" & key_crop_yields$Entity != "Sudan (former)")

lu = subset(land_use, land_use$Code == "" & key_crop_yields$Entity != "Belgium-Luxembourg" & key_crop_yields$Entity != "Ethiopia PDR" & key_crop_yields$Entity != "European Union" & key_crop_yields$Entity != "Land Locked Developing Countries" & key_crop_yields$Entity != "Least Developed Countries" & key_crop_yields$Entity != "Low Income Food Deficit Countries" & key_crop_yields$Entity != "Net Food Importing Developing Countries" & key_crop_yields$Entity != "Pacific Islands Trust Territory" & key_crop_yields$Entity != "Small island developing States" & key_crop_yields$Entity != "Sudan (former)" & key_crop_yields$Entity != "Sudan (former)")

al = subset(arable_land, arable_land$Code == "")
```


### Data Dictionary

# `key_crop_yields.csv`

|variable                         |class     |description |
|:--------------------------------|:---------|:-----------|
|Entity                           |character | Country or Region Name |
|Code                             |character | Country Code (note is NA for regions/continents) |
|Year                             |double    | Year |
|Wheat (tonnes per hectare)       |double    | Wheat yield |
|Rice (tonnes per hectare)        |double    | Rice Yield |
|Maize (tonnes per hectare)       |double    | Maize yield |
|Soybeans (tonnes per hectare)    |double    | Soybeans yield |
|Potatoes (tonnes per hectare)    |double    | Potato yield |
|Beans (tonnes per hectare)       |double    | Beans yield|
|Peas (tonnes per hectare)        |double    | Peas yield |
|Cassava (tonnes per hectare)     |double    | Cassava (yuca) yield|
|Barley (tonnes per hectare)      |double    | Barley|
|Cocoa beans (tonnes per hectare) |double    | Cocoa |
|Bananas (tonnes per hectare)     |double    | Bananas |

# `arable_land`

|variable                                                               |class     |description |
|:----------------------------------------------------------------------|:---------|:-----------|
|Entity                           |character | Country or Region Name |
|Code                             |character | Country Code (note is NA for regions/continents) |
|Year                             |double    | Year |
|Arable land needed to produce a fixed quantity of crops ((1.0 = 1961)) |double    | Arable land normalized to 1961 |


# `fertilizer`

|variable                                        |class     |description |
|:-----------------------------------------------|:---------|:-----------|
|Entity                           |character | Country or Region Name |
|Code                             |character | Country Code (note is NA for regions/continents) |
|Year                             |double    | Year |
|Cereal yield (tonnes per hectare)               |double    | Cereal yield in tonnes per hectare |
|Nitrogen fertilizer use (kilograms per hectare) |double    | Nitrogen fertilizer use kg per hectare |

# `land_use`

|variable                                                  |class     |description |
|:---------------------------------------------------------|:---------|:-----------|
|Entity                           |character | Country or Region Name |
|Code                             |character | Country Code (note is NA for regions/continents) |
|Year                             |double    | Year |
|cereal yield index                                        |double    | Cereal yield index |
|change to land area used for cereal production since 1961 |double    | Change to land area use for cereal production relative since 1961|
|total population (gapminder)                              |double    | Total population from gapminder data |


